Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-17 paper/main.tex
Subject -> Participant

\noindent General
\begin{itemize}
    \item van den Hurk (2017): uses sounds (1.8sec); one-back-task; no
        significant results; but ``sensitivity maps'' and cross-modal and
        cross-subject classification; mentions in a half sentence ``the auditory
        trials might activate only a subset of voxels that contain categorical
        information, whereas the visual trials activate the majority of VTC
        voxels''.
\end{itemize}

@@

\noindent Data Citations, Code Availability
\begin{itemize}
    \item https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880i
    \item cf. other Scientific Data analysis paper
\end{itemize}

@@

% brain mapping via fMRI
Studies in the field of neuropsychology and neuroimaging (e.g.
\citep{penfield1950cerebral, fox1984noninvasive}) have shown that different
parts of the brain are specialized for different perceptual and cognitive
functions.
% occipital cortex for vision -> two pathways
The occipital cortex is considered to be primarily involved in the early stages
of visual perception and giving rise to two distinct pathways that process
different kind of visual information:
% dorsal vs ventral pathway
a dorsal stream (the ``where pathway'') that leads into the parietal lobe, and a
ventral stream (the ``what pathway'') that leads into into the temporal lobe
\citep{goodale1992separate, mishkin1982contribution}.
% PPA
A classic example of a higher-level visual area in the ventral pathway is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{epstein2008parahippocampal}.
% neural correlate of scene perception
Increased hemodynamic activity is observed in the PPA when subjects view
pictures of landscapes, buildings or landmarks (compared to e.g. pictures of
faces or tools) during blood oxygenation level-dependent functional magnetic
resonance imaging (BOLD fMRI) \citep{aguirre1998area, epstein2014neural,
epstein1998ppa, troiani2012object}.

@@

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% three things in common
All reviewed studies share three common aspects:
% designed stimulus set
First, they employed a small sets of carefully chosen and conceptualized
stimuli.
% block-design & task
Second, studies used block-design paradigms to maximize detection power.
Further, they usually employed an explicit (perceptual) judgement task.
% conceptualized stimuli and block: disadvantages
Block-design studies that use conceptualized stimuli and a task have the
advantage of controlling confounding variables (e.g. color, luminance, size,
spatial frequencies, sentence length), maximizing detection power, and keeping
participants paying attention to the stimuli.
% conceptualized stimuli and block: disadvantages
Nevertheless, small sets of conceptualized stimuli and block-design paradigms
lack external and ecological validity \citep{westfall2016fixing,
hasson2004intersubject} because they poorly resemble how we, free of an
explicit perceptual task, experience our rich/multidimensional and continuous
environment that our brains are accommodated to
\citep{sonkusare2019naturalistic}.
% Moreover, study participants can and will become aware about which perceptual
% process is examined in the study by merely being exposed to the experimental
% paradigm.
Third, the reviewed studies averaged results across 7-11 subjects.
% averaging pros and cons
The averaging approach improves signal-to-noise ratio (SNR) but does not
characterize brain functions at an individual level, a prerequisite for the
application of brain imaging methods in individual diagnostics (cf.
\cite{dubois2016building, eickhoff2020towards}).

@@

% hypo a
We hypothesized that whole-brain analyses would reveal increased hemodynamic
activity in the PPA as functionally defined by a
conventional visual localizer for each individual, because all three operationalization capitalize
on events that should evoke the cognitive processing of spatial information.
% hypo b: individuals
We hypothesized further that an exclusively auditory stimulus could localize a
``visual area'' in individual subjects,
% application in individuals
and may offer an alternative paradigm to assess this aspect of brain function
in visually impaired individuals.

@@

% intro
We used three components of the publicly available
\href{http://www.studyforrest.org}{studyforrest.org} dataset that has already
been used by other research groups in independent studies (e.g.
\citep{ben2018hippocampal, jiahui2019predicting, hu2017decoding,
lettieri2019emotionotopy, nguyen2016integration}).
% used studies
The same subjects were
% AD
a) listening to the audio-description \citep{hanke2014audiomovie} of
the movie ``Forrest Gump'',
% AV
b) watching the audio-visual movie \citep{hanke2016simultaneous}, and
% VIS
c) participating in a dedicated six-category block-design visual localizer \citep{sengupta2016extension}.
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications. Following is a summary of the most important aspects.

@@

% VIS study picture categories
All stimuli of the block-design localizer study were already used in a previous study
\citep{haxby2011common}.
%
There were 24 unique grayscale images (s. Figure 2 in
\citep{sengupta2016extension}) for each of six stimulus categories:
% category details
faces (cropped from original background presented on a medium-gray background),
bodies (female and male without heads in clothes; medium-gray background),
objects (e.g. binoculars, screw, chair, mug; medium-gray background), houses
(medium-gray background) and outdoor scenes comprising of nature and street
scenes, and phase scrambled images.
% controlled luminance and size
Images were matched in luminance and size of 400$\times$\unit[400]{px}.
% procedure: presentation & instructions
During the experiment, subjects were presented with four block-design runs, with
two \unit[16]{s} blocks per stimulus category in each run.
% temporal progression
Each image was shown for \unit[900]{ms} and images were separated by a fixation
cross lasting \unit[100]{ms}.
% task
Subjects also performed a one-back matching task to keep them attentive.

@@

% intro
We tested our modeled hemodynamic responses based on stimulus annotations by
conducting standard two-level GLM analyses to create
subject-specific results across the 8 segments for every subject and each
stimulus.
% level 3
Subsequent, third-level analyses averaged contrast estimates over subjects.

@@

% alignments single subjects (for Bland-Altman-Plots) 1st level
The GLM analysis that fitted each voxel's time course separately for each
subject and segment was performed in functional space preserving the orientation
of the EPI images.
% two ways of co-registration
Subject-specific BOLD T2* time series were anatomically co-registered in two
ways:
% subject template (for Bland-Altman-Plot of unthresholded maps)
% \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
a) via linear transformation to a subject-specific, study-specific T2* template
(cf. \citep{sengupta2016extension}), and
% group template (for group and individual brain slices)
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
b) via non-linear transformation to a study-specific T2* group template (cf.
\citep{hanke2014audiomovie}).
% MNI152
This group template was co-registered to the MNI 152 template with an affine
transformation (12 degrees of freedom) to facilitate visualization and
identification of cortical structures.

@@

% third level model
The third level analysis which averaged contrast estimates over subjects was
carried out using FLAME stage 1 with automatic outlier detection
\citep{beckmann2003general, woolrich2004multilevel, woolrich2008robust}.
% thresholding
Here again, Z (Gaussianised T/F) statistic images were thresholded using
clusters determined by Z>3.4 and a (corrected) cluster significance threshold of
p=.05 \citep{worsley2001statistical}.
% brain region identification
Brain regions associated with observed clusters were determined with the Jülich
Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment} and the
Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.
% PPA masks
Regions of interest (ROI) masks for individual PPAs and a PPA group mask of
individual PPA overlaps were created from data provided by
\citep{sengupta2016extension}.

@@

\begin{table*}[h!]
\caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
    of the primary $t$-contrast for the audio-visual movie comparing cuts to a
    setting depicted for the first time with cuts within a recurring setting
    (\texttt{vse\_new > vpe\_old}).
    Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
    followed by brain structures from posterior to anterior, and partially
    covered areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
\label{tab:res-av-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3003 & <.00001 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r.
cuneal c., intracalcarine c., bilaterally occipital fusiform g., precuneus,temporal fusiform c., posterior parahippocampal c.  \\
154 & <.00001 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior
lateral occipital c. \\ % 0.000000656
121 & <.00001 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior
lateral occipital cortex \\ % 0.00000769
\bottomrule
\end{tabular}
\end{table*}

% table group results primary AD contrast
\begin{table*}[h!]
    \caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
        of the primary $t$-contrast for the audio-description comparing
        geometry-related nouns to non geometry-related nouns spoken by the
        audio-description's narrator (\texttt{geo, groom > all non-geo}).
        Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
followed by brain structures from posterior to anterior, and partially covered
areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
    \label{tab:res-ao-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
188 & <.00001 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l.
precuneus \\ % 0.0000000596
164 & <.00001 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r. precuneus;
\\ % 0.000000238
83 & .00013 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r. temporal
(occipital) fusiform c.; posterior parahippocampal g. \\ % 0.000128
73 & .00031 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & l. lingual
g.; temporal (occipital) fusiform g., posterior parahippocampal c. \\ % 0.000128
63 & .00082 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & r. superior
lateral occipital c. \\ % 0.000824
37 & .0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & l. superior
lateral occipital c. \\ % 0.0129
\bottomrule
\end{tabular}
\end{table*}

@@

% intro
Third, we investigated result from both naturalistic paradigms on the level of
individual subjects to ensure that the group results are not just a by-product
of the averaging process.
% AD is the real shit
Further, we hypothesized that an exclusively auditory stimulus could localize
the PPA in individual subjects and thus possibly substitute a classic visual
localizer experiment.
% Sengupta et al., 2016; unilateral in sub-04 and sub-20
The visual localizer yielded bilateral parahippocampal clusters in 12 of 14
subjects and an unilateral right clusters in two subjects (cf. Table 3 in
\citep{sengupta2016extension}).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting thresholded $t$-maps
(Z>1.64, p<.05 cluster corrected) of three different $t$-contrasts, and
titrating\todo{??} the $t$-threshold in the range of [2, 3] in until we found an
isolated cluster (cf. Table 3 in that matched the expected anatomical location
based on literature \citep{epstein1998ppa}.

% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we here used the same contrast of
each naturalistic stimulus and the same threshold for all subjects.
% subject space -> NeuroVault
Results of the analyses that were performed in subject-space can be found in the
accompanying dataset (Z>2.3, p<.05 cluster-corrected).
% here report in group space
For better comparisons of subjects, we here report results from the analyses
performed in group space (Z>3.4, p<.05 cluster-corrected).
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary movie
and audio-description $t$-contrast, and the outline of overlapped, individual PPAs
co-registered to the MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts voxels of
significant clusters in almost all subjects.

% AV
Results of the primary movie contrast yielded bilateral clusters in five subjects,
a unilateral right cluster in six subjects (of which one subjects yielded a
unilateral cluster in the visual localizer), and a unilateral left cluster in
one subject.
% difference to dedicated localizer
We find homologous clusters in sub-20, whereas the dedicated visual localizer
yielded only one cluster in the right hemisphere.

% report here in group
Results of the primary audio-description contrast yielded bilateral clusters in nine subjects
that are within or overlapping with the individual PPA.
% subj-04
In sub-04, two homologous clusters are apparent, whereas the dedicated localizer
(and movie stimulus) yielded only one cluster in the right hemisphere.
% sub-09
In sub-09 the analysis yielded one cluster in the left-hemispheric PPA.

\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
    \caption{Fixed-effects individual-level GLM results (Z>3.4, p<.05
        cluster-corrected).
        Individual brains are aligned via non-linear
        transformation to a study-specific T2* group template that is
        co-registered to the MNI152 template with an affine transformation (12
        degrees of freedom).
        The results of the audio-description's primary
        $t$-contrast (blue) that compares geometry related nouns to non-
        geometry related nouns spoken by the narrator
        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
        primary $t$-contrast (blue) that compares cuts to setting depicted for
        the first time with cuts within a recurring setting
        (\texttt{vse\_new > vpe\_old}).
        Black:
        outline of subject-specific PPA ROIs.
        Light gray: The
        audio-description's field of view (cf. \citep{hanke2014audiomovie}).
        To facilitate comparisons across subjects, we chose the same horizontal
        slice (x=-11) for all subjects as this slice depicts voxels of
        significant clusters in almost all subjects.
        The figure does not show voxels of the left cluster of the movie stimulus
        in sub-09 and sub-18, and voxels of the right cluster of the movie
        stimulus in sub-15.}
    \label{fig:subs-thresh-ppa}
\end{figure*}

% Bland-Altman-Plots
To better depict the agreement and difference between the results of the visual
localizer and the primary audio-description contrast, we created a Bland-Altman-Plot for every
subject (see Figure \ref{fig:bland-altman}).
% what it depicts
Each subplot visualizes the mean value and difference (localizer minus audio-description) of
two spatially corresponding voxels in the unthresholded $z$-maps.
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (cf. KDE plot for the x-axes).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show a higher $z$-value in the audio-description stimulus.

\begin{figure*}[h!]
\centering
    \includegraphics[scale=0.27]{figures/subjs_bland-altman.png}
    \caption{Bland-Altman-Plots for individual subjects.
    The x-axes show the means of two spatially corresponding voxels in the
    unthresholded $z$-map of the audio-description's primary contrast and
    unthresholded $z$-map of the visual localizer (KDE plot on the top).
    The y-axes show the difference of two voxels (localizer minus
    audio-description; KDE plot on the right).
    The overlays depict voxels spatially constrained to the
    temporal and occipital cortex (gray; based on probabilistic Jülich
    Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment}),
    PPA overlap of all subjects (blue),
    and individual PPA(s) (red).}
    \label{fig:bland-altman}
\end{figure*}

@@

% previous studies
Previous studies reported increased hemodynamic activity in the PPA when
participants were watching static pictures of landscape compared to pictures of
faces or objects (e.g. \citep{epstein1998ppa, epstein1999parahippocampal})
whereas one study using spoken sentences reported mixed results
\citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we operationalized spatial perception via GLM $t$-contrasts.
% current study: dissimilar
Contrary to previous studies, our current approach is not based on carefully
designed sets of stimuli but based on annotated stimulus features incidentally
occurring in two naturalistic stimuli.
% group AV
On a group level, results for the audio-visual movie show
significantly increased hemodynamic activity spatially overlapping with a
traditionally localized PPA but also extending into earlier visual cortices.
% group AD
Results for the audio-description also reveal significant activation in the PPA
but restricted to its anterior part.
% individual level
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and a unilateral cluster
in one subjects.
% meaning: generalization to naturalistic stimuli
Results suggest that increased activation in the PPA during the perception of
static pictures generalize to the perception of spatial information embedded in
a movie and an exclusively auditory stimulus.
% meaning: aPPA vs. pPPA
Our results provide further evidence that the PPA can be divided into functional
subregions.
% narrative as substitute
An auditory narrative might substitute a visual paradigm to localize the PPAs
anterior part in visually impaired subjects.

>>>>

@@

\noindent Data Citations, Code Availability, Data Availability

\begin{itemize}
    \item https://www.springernature.com/gp/authors/research-data-policy/data-availability-statements/12330880i
    \item cf. other Scientific Data analysis paper
\end{itemize}

@@

% brain mapping via fMRI
Studies in the field of neuropsychology and neuroimaging (e.g.
\citep{penfield1950cerebral, fox1984noninvasive}) have shown that different
parts of the brain are specialized for different perceptual and cognitive
functions.
% occipital cortex for vision -> two pathways
The occipital cortex is considered to be primarily involved in the early stages
of visual perception and giving rise to two distinct pathways that process
different kind of visual information:
% dorsal vs ventral pathway
a dorsal stream (the ``where pathway'') that leads into the parietal lobe, and a
ventral stream (the ``what pathway'') that leads into into the temporal lobe
\citep{goodale1992separate, mishkin1982contribution}.
% PPA
A classic example of a higher-level visual area in the ventral pathway is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{epstein2008parahippocampal}.
% neural correlate of scene perception
Increased hemodynamic activity is observed in the PPA when participants view
pictures of landscapes, buildings or landmarks (compared to e.g. pictures of
faces or tools) during blood oxygenation level-dependent functional magnetic
resonance imaging (BOLD fMRI) \citep{aguirre1998area, epstein2014neural,
epstein1998ppa, troiani2012object}.

@@

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% three things in common
All reviewed studies share three common aspects:
% designed stimulus set
First, they employed a small sets of carefully chosen and conceptualized
stimuli.
% block-design & task
Second, studies used block-design paradigms to maximize detection power.
Further, they usually employed an explicit (perceptual) judgement task.
% conceptualized stimuli and block: disadvantages
Block-design studies that use conceptualized stimuli and a task have the
advantage of controlling confounding variables (e.g. color, luminance, size,
spatial frequencies, sentence length), maximizing detection power, and keeping
participants paying attention to the stimuli.
% conceptualized stimuli and block: disadvantages
Nevertheless, small sets of conceptualized stimuli and block-design paradigms
lack external and ecological validity \citep{westfall2016fixing,
hasson2004intersubject} because they poorly resemble how we, free of an
explicit perceptual task, experience our rich, multidimensional and continuous
environment that our brains are accommodated to
\citep{sonkusare2019naturalistic}.
% Moreover, study participants can and will become aware about which perceptual
% process is examined in the study by merely being exposed to the experimental
% paradigm.
Third, the reviewed studies averaged results across 7-11 participants.
% averaging pros and cons
The averaging approach improves signal-to-noise ratio (SNR) but does not
characterize brain functions at an individual level, a prerequisite for the
application of brain imaging methods in individual diagnostics (cf.
\cite{dubois2016building, eickhoff2020towards}).

@@

% hypo a
We hypothesized that whole-brain analyses would reveal increased hemodynamic
activity in the PPA as functionally defined by a
conventional visual localizer for each individual, because all three operationalization capitalize
on events that should evoke the cognitive processing of spatial information.
% hypo b: individuals
We hypothesized further that an exclusively auditory stimulus could localize a
``visual area'' in individuals,
% application in individuals
and may offer an alternative paradigm to assess this aspect of brain function
in visually impaired individuals.

@@

% intro
We used three components of the publicly available
\href{http://www.studyforrest.org}{studyforrest.org} dataset that has already
been used by other research groups in independent studies (e.g.
\citep{ben2018hippocampal, jiahui2019predicting, hu2017decoding,
lettieri2019emotionotopy, nguyen2016integration}).
% used studies
The same participants were
% AD
a) listening to the audio-description \citep{hanke2014audiomovie} of
the movie ``Forrest Gump'',
% AV
b) watching the audio-visual movie \citep{hanke2016simultaneous}, and
% VIS
c) participating in a dedicated six-category block-design visual localizer \citep{sengupta2016extension}.
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications. Following is a summary of the most important aspects.

@@

% VIS study picture categories
All stimuli of the block-design localizer study were already used in a previous study
\citep{haxby2011common}.
%
There were 24 unique grayscale images (s. Figure 2 in
\citep{sengupta2016extension}) for each of six stimulus categories:
% category details
faces (cropped from original background presented on a medium-gray background),
bodies (female and male without heads in clothes; medium-gray background),
objects (e.g. binoculars, screw, chair, mug; medium-gray background), houses
(medium-gray background) and outdoor scenes comprising of nature and street
scenes, and phase scrambled images.
% controlled luminance and size
Images were matched in luminance and size of 400$\times$\unit[400]{px}.
% procedure: presentation & instructions
During the experiment, participants were presented with four block-design runs, with
two \unit[16]{s} blocks per stimulus category in each run.
% temporal progression
Each image was shown for \unit[900]{ms} and images were separated by a fixation
cross lasting \unit[100]{ms}.
% task
Participants also performed a one-back matching task to keep them attentive.

@@

% intro
We tested our modeled hemodynamic responses based on stimulus annotations by
conducting standard two-level GLM analyses to create
participant-specific results across the 8 segments for every participant and each
stimulus.
% level 3
Subsequent, third-level analyses averaged contrast estimates over participants.

@@

% alignments single subjects (for Bland-Altman-Plots) 1st level
The GLM analysis that fitted each voxel's time course separately for each
participant and segment was performed in functional space preserving the orientation
of the EPI images.
% two ways of co-registration
Participant-specific BOLD T2* time series were anatomically co-registered in two
ways:
% subject template (for Bland-Altman-Plot of unthresholded maps)
% \href{"https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/sub-01/bold3Tp2/brain.nii.gz"}{example})
a) via linear transformation to a participant-specific, study-specific T2* template
(cf. \citep{sengupta2016extension}), and
% group template (for group and individual brain slices)
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms/blob/master/templates/grpbold3Tp2/brain.nii.gz"
b) via non-linear transformation to a study-specific T2* group template (cf.
\citep{hanke2014audiomovie}).
% MNI152
This group template was co-registered to the MNI 152 template with an affine
transformation (12 degrees of freedom) to facilitate visualization and
identification of cortical structures.

@@

% third level model
The third level analysis which averaged contrast estimates over participants was
carried out using FLAME stage 1 with automatic outlier detection
\citep{beckmann2003general, woolrich2004multilevel, woolrich2008robust}.
% thresholding
Here again, Z (Gaussianised T/F) statistic images were thresholded using
clusters determined by Z>3.4 and a (corrected) cluster significance threshold of
p=.05 \citep{worsley2001statistical}.
% brain region identification
Brain regions associated with observed clusters were determined with the Jülich
Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment} and the
Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.
% PPA masks
Regions of interest (ROI) masks for individual PPAs and a PPA group mask of
individual PPA overlaps were created from data provided by
\citep{sengupta2016extension}.

@@

\begin{table*}[h!]
\caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
    of the primary $t$-contrast for the audio-visual movie comparing cuts to a
    setting depicted for the first time with cuts within a recurring setting
    (\texttt{vse\_new > vpe\_old}).
    Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
    followed by brain structures from posterior to anterior, and partially
    covered areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
\label{tab:res-av-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r.
cuneal c., intracalcarine c., bilaterally occipital fusiform g., precuneus,temporal fusiform c., posterior parahippocampal c.  \\
154 & 0.000000656 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
121 & 0.00000769 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
\bottomrule
\end{tabular}
\end{table*}

% table group results primary AD contrast
\begin{table*}[h!]
    \caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
        of the primary $t$-contrast for the audio-description comparing
        geometry-related nouns to non geometry-related nouns spoken by the
        audio-description's narrator (\texttt{geo, groom > all non-geo}).
        Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
followed by brain structures from posterior to anterior, and partially covered
areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
    \label{tab:res-ao-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
188 & 0.0000000596 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l. precuneus \\
164 & 0.000000238 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r. precuneus; \\
83 & 0.000128 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r. temporal (occipital) fusiform c.; posterior parahippocampal g. \\
73 & 0.000318 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & l. lingual g.; temporal (occipital) fusiform g., posterior parahippocampal c. \\
63 & 0.000824 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & r. superior lateral occipital c. \\
37 & 0.0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & l. superior lateral occipital c. \\
\bottomrule
\end{tabular}
\end{table*}

@@

% intro
Third, we investigated result from both naturalistic paradigms on the level of
individual participants to ensure that the group results are not just a by-product
of the averaging process.
% AD is the real shit
Further, we hypothesized that an exclusively auditory stimulus could localize
the PPA in individual participants and thus possibly substitute a classic visual
localizer experiment.
% Sengupta et al., 2016; unilateral in sub-04 and sub-20
The visual localizer yielded bilateral parahippocampal clusters in 12 of 14
participants and an unilateral right clusters in two participants (cf. Table 3 in
\citep{sengupta2016extension}).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting thresholded $t$-maps
(Z>1.64, p<.05 cluster corrected) of three different $t$-contrasts, and
titrating\todo{??} the $t$-threshold in the range of [2, 3] in until we found an
isolated cluster (cf. Table 3 in that matched the expected anatomical location
based on literature \citep{epstein1998ppa}.

% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we here used the same contrast of
each naturalistic stimulus and the same threshold for all participants.
% subject space -> NeuroVault
Results of the analyses that were performed in participant-space can be found in the
accompanying dataset (Z>2.3, p<.05 cluster-corrected).
% here report in group space
For better comparisons of participants, we here report results from the analyses
performed in group space (Z>3.4, p<.05 cluster-corrected).
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary movie
and audio-description $t$-contrast, and the outline of overlapped, individual PPAs
co-registered to the MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts voxels of
significant clusters in almost all participants.

% AV
Results of the primary movie contrast yielded bilateral clusters in five participants,
a unilateral right cluster in six participants (of which one participant yielded a
unilateral cluster in the visual localizer), and a unilateral left cluster in
one participant.
% difference to dedicated localizer
We find homologous clusters in sub-20, whereas the dedicated visual localizer
yielded only one cluster in the right hemisphere.

% report here in group
Results of the primary audio-description contrast yielded bilateral clusters in nine participants
that are within or overlapping with the individual PPA.
% subj-04
In sub-04, two homologous clusters are apparent, whereas the dedicated localizer
(and movie stimulus) yielded only one cluster in the right hemisphere.
% sub-09
In sub-09 the analysis yielded one cluster in the left-hemispheric PPA.

\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
    \caption{Fixed-effects individual-level GLM results (Z>3.4, p<.05
        cluster-corrected).
        Individual brains are aligned via non-linear
        transformation to a study-specific T2* group template that is
        co-registered to the MNI152 template with an affine transformation (12
        degrees of freedom).
        The results of the audio-description's primary
        $t$-contrast (blue) that compares geometry related nouns to non-
        geometry related nouns spoken by the narrator
        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
        primary $t$-contrast (blue) that compares cuts to setting depicted for
        the first time with cuts within a recurring setting
        (\texttt{vse\_new > vpe\_old}).
        Black:
        outline of participant-specific PPA ROIs.
        Light gray: The
        audio-description's field of view (cf. \citep{hanke2014audiomovie}).
        To facilitate comparisons across participants, we chose the same horizontal
        slice (x=-11) for all participants as this slice depicts voxels of
        significant clusters in almost all participants.
        The figure does not show voxels of the left cluster of the movie stimulus
        in sub-09 and sub-18, and voxels of the right cluster of the movie
        stimulus in sub-15.}
    \label{fig:subs-thresh-ppa}
\end{figure*}

% Bland-Altman-Plots
To better depict the agreement and difference between the results of the visual
localizer and the primary audio-description contrast, we created a Bland-Altman-Plot for every
participant (see Figure \ref{fig:bland-altman}).
% what it depicts
Each subplot visualizes the mean value and difference (localizer minus audio-description) of
two spatially corresponding voxels in the unthresholded $z$-maps.
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (cf. KDE plot for the x-axes).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show a higher $z$-value in the audio-description stimulus.

\begin{figure*}[h!]
\centering
    \includegraphics[scale=0.27]{figures/subjs_bland-altman.png}
    \caption{Bland-Altman-Plots for individual participants.
    The x-axes show the means of two spatially corresponding voxels in the
    unthresholded $z$-map of the audio-description's primary contrast and
    unthresholded $z$-map of the visual localizer (KDE plot on the top).
    The y-axes show the difference of two voxels (localizer minus
    audio-description; KDE plot on the right).
    The overlays depict voxels spatially constrained to the
    temporal and occipital cortex (gray; based on probabilistic Jülich
    Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment}),
    PPA overlap of all participants (blue),
    and individual PPA(s) (red).}
    \label{fig:bland-altman}
\end{figure*}

@@

% previous studies
Previous studies reported increased hemodynamic activity in the PPA when
participants were watching static pictures of landscape compared to pictures of
faces or objects (e.g. \citep{epstein1998ppa, epstein1999parahippocampal})
whereas one study using spoken sentences reported mixed results
\citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we operationalized spatial perception via GLM $t$-contrasts.
% current study: dissimilar
Contrary to previous studies, our current approach is not based on carefully
designed sets of stimuli but based on annotated stimulus features incidentally
occurring in two naturalistic stimuli.
% group AV
On a group level, whole brain-analysis results for the audio-visual movie show
significantly increased hemodynamic activity spatially overlapping with a
traditionally localized PPA but also extending into earlier visual cortices.
% group AD
Results for the audio-description also reveal significant activation in the PPA
but restricted to its anterior part.
% individual level
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine participants and a unilateral cluster
in one participant.
% meaning: generalization to naturalistic stimuli
Results suggest that increased activation in the PPA during the perception of
static pictures generalize to the perception of spatial information embedded in
a movie and an exclusively auditory stimulus.
% meaning: aPPA vs. pPPA
Our results provide further evidence that the PPA can be divided into functional
subregions.
% narrative as substitute
An auditory narrative might substitute a visual paradigm to localize the PPAs
anterior part in visually impaired participants.
